Automated Verification of Stand-alone Solar Photovoltaic Systems

### 2019-04-08 Tex/elsevier/trindade_ren_and_sust_rev1.tex
added comments
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

Configurable program analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting. The CPA formalism provides an interface for the definition of program analyses; consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework. The comparison of different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and interpolation procedures, such that the CPA operators can be written in a concise and convenient way~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as an SMT solver, and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}. CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing. For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs. In software verification, it is usual to take a considerable amount of effort to convert a verification idea into actual experimental results and CPAchecker aims to accelerate this process~\cite{Beyer2011}.
%
%--------------------------------------------------
\section{Stand-alone PV System Sizing and Verification}
\label{sec:sizingcheck}
%--------------------------------------------------
In addition to the verification tool being able to check a PV solar system, as if it were actually being used in the field, indicating the conditions that it does not meet the system user requirements, it is possible to extend the tool, giving it the capacity to carry out the validation of the designed system (a.k.a. sizing check).
%In addition the fact that the automated verification tool can check the possible failure of the PV system during its use at the field, it is possible as well to use the tool to check if the sizing of the components are correct.

>>>>

Configurable program analysis (CPA) provides a conceptual basis for expressing different verification approaches in the same formal setting. The CPA formalism provides an interface for the definition of program analyses. Consequently, CPAchecker provides an implementation framework that allows the seamless integration of program analyses that are expressed in the CPA framework. The comparison among different approaches in the same experimental setting is intended to be easy and the experimental results are expected to be more meaningful~\cite{Beyer2011}. Related to the architecture, the central data structure is a set of control-flow automata (CFA), which consists of control-flow locations and control-flow edges. The CPA framework provides interfaces to SMT solvers and interpolation procedures~\cite{Beyer2011}. Currently, CPAchecker uses MathSAT as SMT solver; and CSIsat and MathSAT as interpolation procedures~\cite{Beyer2011}. CPAchecker performs reachability analysis and operates on an object of the abstract data type CPA, i.e., the underlying verification algorithm applies operations from the CPA interface without knowing which concrete CPA it is analyzing. For most configurations, the concrete CPA will be a composite CPA, which implements the combination of different CPAs. \textcolor{red}{It is unclear what a CPA is.}
%In software verification, it is usual to take a considerable amount of effort to convert a verification idea into actual experimental results and CPAchecker aims to accelerate this process~\cite{Beyer2011}.
%
%--------------------------------------------------
\section{Stand-alone PV System Sizing and Verification}
\label{sec:sizingcheck}
%--------------------------------------------------
In addition to the verification tool being able to check a PV solar system, as if it were actually being used in the field, indicating the conditions that it does not meet the system user requirements, it is possible to extend the tool, giving it the capacity to carry out the validation of the designed system (a.k.a. sizing check).
%In addition the fact that the automated verification tool can check the possible failure of the PV system during its use at the field, it is possible as well to use the tool to check if the sizing of the components are correct.
